---
title: "03-2 Problem Set"
author: 
format: pdf
---

Complete the following, replacing the *italic* text. Knit this document to a pdf, **double check the pdf document for errors**, and submit this to this week's Problem Set assignment on Canvas. 

## Problem 1 - Function

Below write a function that converts a flowrate of ftˆ3/second to mˆ3/s and make sure it can handle `NA` values. Remember this from last week? Just make your code into a function, but make sure to use descriptive names for your function and arguments and make sure your code is formatted nicely with "Code>Reformat Code". 
 

```{r}
# Answer here
```

## Problem 2 - Packages

Find a package in the CRAN or bioconductor that you think you might use in a future class, or job, or project. 

What is the name of your chosen package? 

*answer here*

What is the Description of your chosen package?

*answer here*

Why did you choose this package?

*answer here*

Does your package have a vignette? If so does it seem helpful after a quick skim?

*answer here*

What are the key functions in the package? What is their usage and key arguments?

*answer here*

Provide a useful-to-you example from one of the functions documentation that you read.

```{r}
#Answer here
```

What was not helpful or unclear about the package documentation? 

*answer here*

## Problem 3 - Using comments

Add comments after each line of the following code to explain what it does. Use the help documentation of functions you don't know. 

```{r}
compute.stat <- function(xvec) {
  ave <- mean(xvec)
  var <- var(xvec)
  CV <- sqrt(var)/ave  #CV is sd/mean
  cat(ave, var, CV, "\n") 
  out <- list(ave=ave, var=var, sd=sqrt(var), CV=CV)
  return(out)
}
```


## Problem 4 - Debugging

Debug the following code which is meant to calculate summary statistics of several measurements of iris flowers. Comment out the broken code, copy and paste each line on a new line, then fix it. Add a comment underneath each fixed line about what was wrong.  

```{r}
iris

# mean sepal width
mean(Sepal.Width) 

# mean sepal width of setosa species
mean(iris[iris$Species == "setosa", "Sepal.Width"]
     
# mean sepal width of versicolor species
mean(iris[iris$Species == setosa, "Sepal.Width"])
     
# mean sepal width of virginica species
mean(iris[iris$Species = "virginica", "Sepal.Width"])

```

